Computational Prediction of Boundaries of 3D Genomic Domains in Class Imbalance Settings

### 2019-08-27 Manuscript/manuscript.Rmd
results edits

Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [??? I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution. The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50. The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.06, 0.10, 0.14, 0.12, and 0.06 [??? Add exact numbers, like $18.34 \pm 5.06 \%$] for the Gm12878 data at 5 kb, 10 kb, 25 kb, 50 kb, and 100 kb resolutions, respectively, with similar results observed for the K562 cell line  (Supplementary Figure 3). The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.

>>>>

Given that the number of bins annotated as TAD boundaries (TAD boundary regions) is much smaller than the number of non-TAD boundary bins, we investigated the class imbalance (CI) [??? I changed PI to CI - change in supplementary accordingly; !!!fixed] featured at each resolution. The CI was defined as the ratio of TAD boundary regions ($Y=1$) versus the sum of both TAD and non-TAD boundary regions and ranging from 0 to 0.50. The CI was found to be invariant to resolution, remaining consistently low across chromosomes, with an average of 0.196 (SD=0.025) and 0.166 (SD=0.026) for the GM12878 and K562 cell lines, respectively [??? Add exact numbers, like $18.34 \pm 5.06 \%$ !!!added] (Supplementary Figure 3). The presence of class imbalance justifies the the need for using resampling techniques before predictive modeling.
